### 2016-03-12 paper/stereo.tex
Hang

@@

>>>>

\hang{Better to explain the methology we used, either here or in
  Result part. For example:}

\hang{To evaluate the effectness of different parallel structures, we
  plot the energy minimization process against time. We define the
  energy of the parallel system at a certain time as the minimum
  energy of all threads at that time.}

@@

Since the optimization in the above stereo problem is fairly easy, we
compare our method with both parallel alpha expansion
\cite{first_fusion_viktor} and hierarchy fusion \cite{olga}.
